Groth16 zk-SNARK Proof Verification on Freeton : Three Use Cases

### 2021-07-14 submission/submission.tex
add pincode image, early pointers to ft

\begin{description}
	\item[Code:] All our code comes with a README, standard
          in-code documentation and tests. This document is provided
          as an overview of our use cases for \zksnarks{} on the
          Freeton blockchain but you can also directly dive into the
          code. All our code is under the GPL license and is hosted at
          \url{https://github.com/OCamlPro/devex-18-zk-contest}.

@@

	\item[Keys on contracts: ] In the Euler and Pincode smart
          contracts, we provided, along with the verification key as
          needed by the \verb|vergroth16| instruction, the proving key
          (in a zipped format) on the smart contract. This enables
          users to easily find it in order to generate their
          proofs. In case the contract deployer should decide to keep
          the possibility of changing the verification and proving
          keys of the problem(s), this also makes it easiest to follow
          changes before submitting a solution. Unfortunately, the
          proving key for the Sudoku has size 64KB (19KB after
          compression) which is about 6 times (respectively 10 times
          once zipped) bigger than for Euler and Pincode, and we
          decided not to include it.

@@

    \end{lstlisting}
\end{description}

@@

	\item \verb|EulerUser|: it's the contract corresponding to the
        pubkey of a user. The user can provide a name using the
        \verb|set_name()| function.  The \verb|has_solved()| function
        is called by the \verb|EulerRoot| contract when the user has
        solved a new problem. The function stores the problem and the
        time of solution in the contract.

	For internal messages between these contracts, they either check that
	messages are coming from the unique \verb|EulerRoot| contract, or that they
	come from pre-computed addresses à la TIP-3.

@@

@@

\section{Thoughts on three paradigms of \zksnarks{} on blockchains}
\label{sec_three_paradigms}
This contest has given us the opportunity to think harder about the categories of uses of \zksnarks{} on blockchains:
\begin{enumerate}
	\item Statically checking that someone has some information at their disposal(Euler case)
	\item Encoding a possibly complex computation in a circuit and challenging a user with an instance of that computation (Sudoku case)
	\item Using the \zksnark{} as an extension of the blockchain protocol itself (pincode, anonymous transactions, voting protocols)
\end{enumerate}

>>>>

\begin{description}
        \item[ft:] Throughout this project, we make heavy use of our
          in-house freeton wallet and client \verb|ft|. We have taken
          extra care to make its use very simple, using docker images
          and intuitive, well-documented features. We have specially
          adapted this tool to be able to create local sandboxes using
          the Nil Foundation's fork of the TON OS, as well as to
          interact with the Nil foundation server. Please check out
          \url{https://hub.docker.com/r/ocamlpro/ft}. The
          documentation is available both in the command line through
          \verb|ft --help| and on the website
          \url{https://ocamlpro.github.io/freeton_wallet/sphinx/}.

	\item[Code:] All our code comes with a README, standard
          in-code documentation and tests. This document is provided
          as an overview of our use cases for \zksnarks{} on the
          Freeton blockchain but you can also directly dive into the
          code. All our code is under the GPL license and is hosted at
          \url{https://github.com/OCamlPro/devex-18-zk-contest}.

@@

	\item[Keys on contracts: ] In the Euler and Pincode smart
          contracts, we provided, along with the verification key as
          needed by the \verb|vergroth16| instruction, the proving key
          (in a zipped format) on the smart contract. This enables
          users to easily find it in order to generate their
          proofs. In case the contract deployer should decide to keep
          the possibility of changing the verification and proving
          keys of the problem(s), this also makes it easiest to follow
          changes before submitting a solution. Unfortunately, the
          proving key for Sudoku is an order of magnitude bigger than
          for Euler and Pincode (even zipped), and we decided not to
          include it.

@@

@@

	\item \verb|EulerUser|: it's the contract corresponding to the
        pubkey of a user. The user can provide a name using the
        \verb|set_name()| function.  The \verb|has_solved()| function
        is called by the \verb|EulerRoot| contract when the user has
        solved a new problem. The function stores the problem and the
        time of solution in the contract.
\end{enumerate}
	For internal messages between these contracts, they either check that
	messages are coming from the unique \verb|EulerRoot| contract, or that they
	come from pre-computed addresses à la TIP-3.

@@

	\begin{figure}[!h]
	\centering
	\includegraphics[width=0.6\textwidth]{pincode}
	\end{figure}

@@

\section{Thoughts on three paradigms of \zksnarks{} on blockchains}
\label{sec_three_paradigms}
We wish to conclude with some broader considerations. This contest has
given us the opportunity to think harder about the categories of uses
of \zksnarks{} on blockchains:
\begin{enumerate}
	\item Statically checking that someone has some information at their disposal(Euler case)
	\item Encoding a possibly complex computation in a circuit and challenging a user with an instance of that computation (Sudoku case)
	\item Using the \zksnark{} as an extension of the blockchain protocol itself (pincode, anonymous transactions, voting protocols)
\end{enumerate}
